### 2014-02-22 paper/retrofit.tex
wip

\begin{mathpar}
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iconf iS (lconf id il tS (iniE (IT te)), ldots)
.->
iconf iS (lconf id il tS' (iniE (IT te')), ldots)
|}

\and
\inferrule[I-getLabel]
{ }
{|
iconf iS (lconf id il tS (iniE (getLabel)), ldots)
.->
iconf iS (lconf id il tS (iniE il), ldots)
|}

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
.->
iconf iS (lconf id il' tS (iniE unit), ldots)
|}

@@

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
.->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[id mapsto io1 , ... , iok]|\\
| ie1'' = {ie'/ix1,id'/ix2} ie1|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
.->
iconf iS' (lconf id il tS (iniE ie1''), ldots)
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
.->
iconf iS' (lconf id il tS (iniE ie2), ldots)
|}

\inferrule[I-pure]
{| ie .~> ie'|}
{|
  iconf iS (lconf id il tS (iniE ie))
.->
iconf iS (lconf id il tS (iniE ie))
|}

\and
\inferrule[I-labelOp]
{ |denot (il lop il') = iv|}
{ |il lop il' .~> iv| }

\and
\inferrule[I-border]
{ } {| IT (TI (ie)) .~> ie |}

>>>>

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (lconf id il tS ie, ldots)
.->
iconf iS' (lconf id il' tS' ie', ldots)
|}
{|
iconf iS (lconf id il tS (iniE ie), ldots)
.->
iconf iS' (lconf id il' tS' (iniE ie'), ldots)
|}

\and
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iconf iS (lconf id il tS (IT te), ldots)
.->
iconf iS (lconf id il tS' (IT te'), ldots)
|}

%% \and
%% \inferrule[I-getLabel]
%% { }
%% {|
%% iconf iS (lconf id il tS getLabel, ldots)
%% .->
%% iconf iS (lconf id il tS il, ldots)
%% |}

\and
\inferrule[I-getLabel]
{ }
{|
iconf iS (inTE id il getLabel)
.->
iconf iS (inTE id il il)
|}

%% \and
%% \inferrule[I-setLabel]
%% { |il canFlowTo il'| }
%% {|
%% iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
%% .->
%% iconf iS (lconf id il' tS (iniE unit), ldots)
%% |}

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (inTE id il (setLabel il'))
.->
iconf iS (inTE id il' unit)
|}

@@

%% \and
%% \inferrule[I-send]
%% {
%% |il canFlowTo il'|\\
%% |iS(id') = Q|\\
%% |iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
%% }
%% {|
%% iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
%% .->
%% iconf iS' (lconf id il tS (iniE unit), ldots)
%% |}

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
}
{|
iconf iS  (inTE id il (send id' il' ie))
.->
iconf iS' (inTE id il unit)
|}

%% \and
%% \inferrule[I-recv]
%% {
%% | filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
%% | iS' = iS[id mapsto io1 , ... , iok]|\\
%% | ie1'' = {ie'/ix1,id'/ix2} ie1|
%% }
%% {|
%% iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
%% .->
%% iconf iS' (lconf id il tS (iniE ie1''), ldots)
%% |}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[id mapsto io1 , ... , iok]|\\
}
{|
iconf iS  (inTE id il (ix1, ix2 <= recv. ie1 ie2))
.->
iconf iS' (inTE id il ({ie'/ix1,id'/ix2} ie1))
|}

%% \and
%% \inferrule[I-noRecv]
%% {
%% | filter il (iS(id)) = nil|\\
%% | iS' = iS[id mapsto nil]|
%% }
%% {|
%% iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
%% .->
%% iconf iS' (lconf id il tS (iniE ie2), ldots)
%% |}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS  (inTE id il (ix1, ix2 <= recv. ie1 ie2))
.->
iconf iS' (inTE id il ie2)
|}

\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |iconf iS (inTE id il (il1 lop il2)) .-> iconf iS (inTE id il iv)| }

\and
\inferrule[I-border]
{ }
{|
iconf iS (inTE id il (IT (TI (ie))))
.->
iconf iS (inTE id il ie)
|}
